\textbf{Discovery of a disrupting open cluster in the Galactic halo:\\ a recent star formation event in the leading arm of the Magellanic stream}

### 2018-11-03 ms.tex
captions and data section

We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
\figurename~\ref{fig:cmds} shows the \gaia\ data for this region.
The left panel of \figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}: Surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as markers (blue).

The \gaia\ data demonstrate the presence of a co-moving, clustered over-density of blue stars, but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
With the \gaia\ data alone, the distance, age, and metallicity of the cluster therefore cannot be determined, as these quantities are degenerate where the main sequence is nearly vertical.
In the next section, we describe deeper \decam\ imaging obtained over a portion of the cluster.

% Notebook: Figure-CMDs
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/gaia-cmd-pm.pdf}
\caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
\textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
Blue markers show only sources in the blue selection polygon shown in the CMD (left panel).
\textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
Blue markers again show only sources in the blue CMD selection region (left panel).
}
\label{fig:cmds}
\end{figure}

@@

\todo{Nidever}

% Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
% a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
% is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
% The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.  Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths:2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever:2008}.
% The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
% position of the cluster.
% Yumi:
% Need a sentence or two for dust extinction correction somewhere in the above two paragraphs?

% Notebook: Figure-DECam-CMD
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/DECam-cmd.pdf}
\caption{TODO}
\label{fig:decam-cmd}
\end{figure}

@@

\subsection{Determining kinematic membership}
\label{sec:pmclean}

>>>>

We then query all objects from the \gaia\ \DR{2} catalog within a rectangle centered on the nominal position of this group, with a width of $5^\circ$ and a height of $5^\circ$ in the equatorial (ICRS) coordinate system (see Appendix~\ref{sec:queries} for the database query).
\figurename~\ref{fig:cmds} shows the \gaia\ data for this region.
The left panel of \figurename~\ref{fig:cmds} shows the \gaia\ color-magnitude diagram, with the blue over-density highlighted by the polygon (blue) and under-plotted with a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone \citep[red line;][]{Dotter:2016, Choi:2016, Paxton:2011, Paxton:2013, Paxton:2015}: Surprisingly, this appears to be a young, distant main sequence, rather than an old population of horizontal branch stars.
The middle and right panels of \figurename~\ref{fig:cmds} show sky positions and proper motions, respectively, of all stars in this sky region (grey background density), and only stars in the CMD selection polygon as black markers.

The \gaia\ data demonstrate the presence of a young, distant, spatially-clustered, and co-moving stellar over-density --- named \clustername\ --- but the \gaia\ photometry is too shallow to resolve anything but the brightest main sequence stars.
With the \gaia\ data alone, the distance, age, and metallicity of the cluster therefore cannot be determined, as these quantities are degenerate where the main sequence is nearly vertical.
In the next section, we describe deeper \decam\ imaging obtained over a portion of the cluster.

% Notebook: Figure-CMDs
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/gaia-cmd-pm.pdf}
\caption{Color-magnitude diagram, sky positions, and proper motions from \gaia\ \DR{2} for the region around $(\alpha, \delta) \sim (179, -29)^\circ$.
\textbf{Left panel}: \gaia\ color-magnitude diagram (CMD) for all sources with $G < 20$ and sky position within 3 degrees of $(\alpha, \delta) = (179.5, -28.8)^\circ$.
Red line shows a $100~\textrm{Myr}$, $\feh = -1.1$ \acronym{MIST} isochrone shifted to a distance of $30~\kpc$.
Shaded pixels (orange) show regions of high density and points (black markers) are plotted when there are fewer than 8 stars per pixel.
\textbf{Middle panel}: Sky positions for all sources in the shown sky region (grey 2D histogram).
Black markers show only sources in the blue selection polygon shown in the CMD (left panel).
\textbf{Right panel}: Proper motions for all sources in the shown sky region (grey 2D histogram).
Black markers again show only sources in the blue CMD selection region (left panel).
}
\label{fig:cmds}
\end{figure}

@@

We obtained \decam\ $u$-, $g$-, and $i$-band imaging of a single field centered on a portion of the cluster discovered using the \gaia\ data (see previous section).
\todo{Nidever: can you describe the observations? Exposure times, dither, whatever is usually done...}

The photometry was reduced...\todo{Nidever: describe your pipeline?}

\figurename~\ref{fig:decam-field} shows the sky positions of the \gaia\ CMD-selected sources (black markers; see same in middle panel, \figurename~\ref{fig:cmds}), along with point sources identified in the $g$-band data obtained with \decam: sources in control fields are shown as red markers, and sources in cluster fields are shown as blue markers.
We note that the smaller over-density located northeast of the \decam\ field was not followed up in this work.

\figurename~\ref{fig:decam-cmd} shows \decam\ color-magnitude diagrams for the control and cluster sub-fields (the magnitudes here are not extinction-corrected).
We find that the $u$-band data were too shallow to be useful for this work, so restrict the further analysis in this work to the $g$- and $i$-bands.
The blue comoving group, \clustername, identified in \sectionname~\ref{sec:discovery} using \gaia\ data alone shows up as a clear young main sequence in the cluster fields (right panel of \figurename~\ref{fig:decam-cmd}).
Later, we use photometry in the sub-region of the cluster fields identified by the dashed rectangle to infer the cluster parameters.

 % Notebook: Figure-DECam-CMD
 \begin{figure}
 \centering
 \includegraphics[width=0.6\textwidth]{figures/DECam-field.pdf}
 \caption{The sky region around \clustername, showing the same \gaia\ CMD-selected sources as in \figurename~\ref{fig:cmds} (black markers), and point sources identified from \decam\ $g$-band follow up (blue and red markers).
 Red markers show sources in the \decam\ field used as control sources, and blue markers show sources used as cluster member candidates.}
 \label{fig:decam-field}
 \end{figure}

% Notebook: Figure-DECam-CMD
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/DECam-cmd.pdf}
\caption{\decam\ $g-i$ versus $g$ color-magnitude diagrams for the \decam\ control fields (left panel) and \decam\ cluster fields (right panel).
Note the prominent young, distant main sequence in the cluster fields: This is the main sequence of \clustername.
The sources in the dashed (red) rectangle in the right panel are later used to measure the cluster stellar population parameters.
}
\label{fig:decam-cmd}
\end{figure}

@@

% TODO: change to just inferring mean proper motion of the cluster!
\subsection{Determining kinematic membership}
\label{sec:pmclean}
